Modeling Two-Dimensional Vesicle Hydrodynamics with Hydrophobic Attraction Potential Simulations

### 2021-09-08 doc/main_jfm.tex
yny Sep07

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{\label{intro}Introduction}
Described by de Gennes as ``another animal in soft matter physics", the
Janus particle (often a spherical particle with a hydrophobic and a
hydrophilic hemisphere) exhibits complex aggregate, clustering, and
self-assembly into mesoscopic and macroscopic structures that are
relevant to a wide range of applications in biology and bioengineering.
Whether it is surface chemistry or polarity under an external field, the
dynamics of Janus particles is inevitably the combination of long-range
hydrodynamics interactions in the presence of short- and
intermediate-range particle-particle interactions. Recently~\cite{Fu20}
illustrated that the hydrophobic interactions between Janus particles in
a viscous solvent can be used as a coarse-grained model to capture the
mechanics of an elastic bilayer membrane of amphiphilic macromolecules
such as lipids. Depending on the total number of Janus particles and
their geometry, in a viscous solvent, Janus particles can aggregate to
form a micelle, a patch of bilayer membrane with open ends, and a
self-enclosed bilayer membrane (referred to as a JP vesicle). Using a
hybrid continuum model for the interactions between amphiphilic
particles in a viscous solvent and with a boundary integral
formulation,~\cite{Fu20} showed that the membrane granularity during
fusion and fission of bilayers can be accurately captured. 
%This boundary integral formulation has inspired more recent work

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{\label{intro}Introduction}
Described by de Gennes as ``another animal in soft matter physics", the
Janus particle (often a spherical particle with a hydrophobic and a
hydrophilic hemisphere) exhibits complex aggregate, clustering, and
self-assembly into mesoscopic and macroscopic structures that are
relevant to a wide range of applications in biology and bioengineering.
Whether it is surface chemistry or polarity under an external field, the
dynamics of Janus particles in a viscous solvent is inevitably the combination of long-range
hydrodynamics interactions with both short- and intermediate-range 
particle-particle interactions. Such multi-scale nature of Janus particle dynamics underlies 
the richness of a Janus particle suspension, as \cite{deGennes1991} suggested by the example of 
a ``thin film of Janus grains" that can breathe due to the interstices between Janus particles.

Recently~\cite{Fu20}
illustrated that the hydrophobic interactions between Janus particles in
a viscous solvent can be used as a coarse-grained model to capture the
mechanics of an elastic bilayer membrane of amphiphilic macromolecules
such as lipids. Depending on the total number of Janus particles and
their geometry, in a viscous solvent, Janus particles can aggregate to
form a micelle, a patch of bilayer membrane with open ends, and a
self-enclosed bilayer membrane (referred to as a JP vesicle). Using a
hybrid continuum model for the interactions between amphiphilic
particles in a viscous solvent and with a boundary integral
formulation,~\cite{Fu20} showed that the membrane granularity during
fusion and fission of bilayers can be accurately captured. 
%This boundary integral formulation has inspired more recent work
